Comparing Interactions Between Collective Bargaining, Wages and Income, and House of Representative Elections

### 2024-01-12 Documents/Paper.qmd
fix graphs

```{r fig-uniondata}
#| echo: false
#| fig-cap: Union Data

@@

## Income Data
```{r fig-incomedata}
#| echo: false
#| fig-cap: Income Data

@@

```{r fig-incomedataadj}
#| echo: false
#| fig-cap: Income Data (adjusted)

@@

```{r fig-wagedata}
#| echo: false
#| fig-cap: Wage Data

@@

```{r fig-housedata}
#| echo: false
#| fig-cap: House Data

@@

```{r fig-unionwagedata}
#| echo: false
#| fig-cap: Union Wage Data

@@

```{r fig-collectivebargain}
#| echo: false
#| fig-cap: Collective Bargain Data

@@

```{r fig-collectivebargaindecade}
#| echo: false
#| fig-cap: Collective Bargain Data by Decade

@@

```{r fig-collectivebargainregion}
#| echo: false
#| fig-cap: Collective Bargain Region by Decade and Region

@@

Our results for these t-tests determine if there is a statistically significant difference between union wages and non union wages in the 1980s and the 2010s.

@@

```{r}
#| echo: FALSE
#| warning: FALSE
#| tbl-cap: Wages by Union and Non Union Workers

>>>>

```{r fig-uniondata}
#| echo: false
#| warning: FALSE
#| fig-cap: Union Data

@@

## Income Data
```{r fig-incomedata}
#| echo: false
#| warning: FALSE
#| fig-cap: Income Data

@@

```{r fig-incomedataadj}
#| echo: false
#| warning: FALSE
#| fig-cap: Income Data (adjusted)

@@

```{r fig-wagedata}
#| echo: false
#| warning: FALSE
#| fig-cap: Wage Data

@@

```{r fig-housedata}
#| echo: false
#| warning: FALSE
#| fig-cap: House Data

@@

```{r fig-unionwagedata}
#| echo: false
#| warning: FALSE
#| fig-cap: Union Wage Data

@@

```{r fig-collectivebargain}
#| echo: false
#| warning: FALSE
#| fig-cap: Collective Bargain Data

@@

```{r fig-collectivebargaindecade}
#| echo: false
#| warning: FALSE
#| fig-cap: Collective Bargain Data by Decade

@@

```{r fig-collectivebargainregion}
#| echo: false
#| warning: FALSE
#| fig-cap: Collective Bargain Region by Decade and Region

@@

Our results seen in @tbl-ttest for these t-tests determine if there is a statistically significant difference between union wages and non union wages in the 1980s and the 2010s.

@@

```{r tbl-ttest}
#| echo: FALSE
#| warning: FALSE
#| tbl-cap: Wages by Union and Non Union Workers
